Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-03 src/paper.tex
update

Discretization methods have been studied for speech enhancement \cite{selm} and blind speech separation \cite{dasb}, however, this approach has been rarely for target speaker extraction. TokenSplit \cite{tokensplit} needs the transcript of the speech to achieve satisfying results. In 
real life, however, speech is rarely provided with its transcript.

>>>>

Discretization methods have been studied for speech 
enhancement \cite{selm} and blind speech separation \cite{dasb,tokensplit}, 
however, this approach has 
been rarely studied for target speaker extraction. Our work focuses on utilizing discrete tokens 
to do target speaker extraction.
